Associations between Chlorophyll \emph{a} and various Microcystin-LR Health Advisory Concentrations

### 2015-09-16 manuscript/manuscript.Rmd
fixed results in-line code

We use this association to identify chlorophyll *a* concentrations that are associated with greater than even odds of exceeding a given health advisory level (Table \ref{tab:mc_chla_table}).  These represent `r 100*(length(nla_dat$CHLA[nla_dat$CHLA>=mc_chla[1]])/length(nla_dat$CHLA))`%, `100*(length(nla_dat$CHLA[nla_dat$CHLA>=mc_chla[2]])/length(nla_dat$CHLA))`%,
`100*(length(nla_dat$CHLA[nla_dat$CHLA>=mc_chla[3]])/length(nla_dat$CHLA))`%, and `100*(length(nla_dat$CHLA[nla_dat$CHLA>=mc_chla[4]])/length(nla_dat$CHLA))`% of sample lakes for the U.S EPA childrens drinking water, the WHO drinking water, the U.S. EPA Adult drinking water, and the WHO recreationsl standards, respecitvely.
<!-- (Figure \ref{fig:chla_micro_cdf}) -->

>>>>

We use this association to identify chlorophyll *a* concentrations that are associated with greater than even odds of exceeding a given health advisory level (Table \ref{tab:mc_chla_table}).  These represent `r round(100*(length(nla_dat$CHLA[nla_dat$CHLA>=mc_chla[1]])/length(nla_dat$CHLA)),1)`%, `r round(100*(length(nla_dat$CHLA[nla_dat$CHLA>=mc_chla[2]])/length(nla_dat$CHLA)),1)`%,
`r round(100*(length(nla_dat$CHLA[nla_dat$CHLA>=mc_chla[3]])/length(nla_dat$CHLA)),1)`%, and `r round(100*(length(nla_dat$CHLA[nla_dat$CHLA>=mc_chla[4]])/length(nla_dat$CHLA)),1)`% of sample lakes for the U.S EPA childrens drinking water, the WHO drinking water, the U.S. EPA Adult drinking water, and the WHO recreationsl standards, respecitvely.
<!-- (Figure \ref{fig:chla_micro_cdf}) -->

### 2015-09-16 manuscript/manuscript.tex
fixed results in-line code

We use this association to identify chlorophyll \emph{a} concentrations
that are associated with greater than even odds of exceeding a given
health advisory level (Table \ref{tab:mc_chla_table}). These represent
27.7831559\%,
\texttt{100*(length(nla\_dat\$CHLA{[}nla\_dat\$CHLA\textgreater{}=mc\_chla{[}2{]}{]})/length(nla\_dat\$CHLA))}\%,
\texttt{100*(length(nla\_dat\$CHLA{[}nla\_dat\$CHLA\textgreater{}=mc\_chla{[}3{]}{]})/length(nla\_dat\$CHLA))}\%,
and
\texttt{100*(length(nla\_dat\$CHLA{[}nla\_dat\$CHLA\textgreater{}=mc\_chla{[}4{]}{]})/length(nla\_dat\$CHLA))}\%
of sample lakes for the U.S EPA childrens drinking water, the WHO
drinking water, the U.S. EPA Adult drinking water, and the WHO
recreationsl standards, respecitvely.

>>>>

We use this association to identify chlorophyll \emph{a} concentrations
that are associated with greater than even odds of exceeding a given
health advisory level (Table \ref{tab:mc_chla_table}). These represent
27.8\%, 11.9\%, 8.3\%, and 7.4\% of sample lakes for the U.S EPA
childrens drinking water, the WHO drinking water, the U.S. EPA Adult
drinking water, and the WHO recreationsl standards, respecitvely.
